Reproducible development environments with rix

### 2023-12-23 paper.qmd
targets github actions

>>>>

If one wishes to run pipelines written using the [targets]{.pkg} [@landau2021]
on Github Actions, [rix]{.pkg} featrues a function called `tar_nix_ga()`,
inspired by the `tar_github_actions()` function from the [targets]{.pkg}
package. This function writes a YAML file under `.github/workflows/` which then
runs the [targets]{.pkg} pipeline using Github Actions at each push, in a
completely reproducible environment. For such an example, consult the
code in this repository^[https://github.com/b-rodrigues/rix_cicd].
